{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-05-02 bmvc_review.tex
KCF section, half-way through.

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and thetheory and its workflowhas been detailed in
other papers already
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevantto thisstudy. Its
computational efficiency arises from its use of the discrete Fourier
transform of the circulant matrix and frequency domain. The KCF
essentially solves the problem of a regression in the form of the
regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} is available by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this
closed-form solution with

Then, the Circulant-matrix based solution vector in the Fourier domain
$\hat{w}$ is formulated as
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To further improve the robustness to geometric and photographic variations, one can exploit non-linear
regression function in the Correlation Filter framework \cite{henriques2015high}. 
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.

>>>>

\subsection{Kernelized Correlation Filter} \label{sec:kcf}
The Kernelized Correlation Filter is a well, known single target
tracking method and thetheory and its workflowhas been detailed in
other papers already
\cite{henriques2012exploiting,henriques2015high}. This section briefly
goes over the parts of the KCF relevantto thisstudy. Its
computational efficiency arises from its use of the discrete Fourier
transform of the circulant matrix and frequency domain. The KCF
essentially solves the problem of a regression in the form of the
regularized ridge regression as:
\begin{equation}
E(h) = \frac{1}{2}||y-\sum_{c=1}^{C}h_{c}*x_{c}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||h_{c}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $y$ represents the desired continuous response whereas $h$ and
$x_{c}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equaiton \ref{eq:Closedform_RidgeReg} can be computed by
taking the derivative of $E$ w.r.t $w$ to $0$. To make this,
$\mathcal{0}(n^{3})$ solution more tractable, an element-wise,
multiplication in frequency domain was proposed as a sub-linear
solution for $\hat{w}$:
\begin{equation}
\hat{w} = \hat{x}^{*}*\hat{y}(\hat{x}^{*}*\hat{x}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
To make the above, closed-form solution more robust to any geometric
and photometric variations, a non-linear version is also proposed
\cite{henriques2015high}.
%\begin{equation}
%\alpha = y(K+\lambda I)^{-1}
%\end{equation}
%where $K$ and $\alpha$ represent the kernel matrix and corresponding
%dual space solution. 
%\cite{henriques2015high} states that kernel
%matrices is circulant for datasets of circular cylic satisfying the
%following theorem.
%\begin{equation}
%k(x,x^{'}) = k(Mx,Mx^{'}),
%\label{eq:KernelCirculantTheorem}
%\end{equation}
%where $M$ represents the permutation matrix. Some kernels satisfying
%the eq.~\ref{eq:KernelCirculantTheorem} are \textit{Gaussian},
%\textit{Polynomial}, \textit{Intersection} and \textit{Hellinger}
%kernels. 
The diagonalized Fourier domain dual form solution can be
expressed as
\begin{equation}
\hat{\alpha} = \hat{y}(\hat{k}^{xx}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\hat{k}^{xx}$ represents the first row of the Kernel matrix $K$
known as \textit{gram matrix} and it is expressed as
\begin{equation}
k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\hat{x}_{c}^{*}\odot \hat{x}_{c}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
%\begin{equation}
%k^{xx^{'}} = exp(-\dfrac{1}{\alpha^{2}}(||x||^{2}+||x^{'}||^{2}-2F^{-1}(\hat{x}^{*}\odot \hat{x}^{'})))
%\label{eq:GaussianCorrelationSingleChannel}
%\end{equation}
The first correlation filter based trackers used grayscale feature ($C=1$) to
learn the solution vector $w$, however, multi-channel features
such as HoG and Color were later exploited to improve tracking
accuracy \cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
\begin{comment}The multi-channel feature integration into the Gaussian Kernelization
function in eq.~\ref{eq:GaussianCorrelationSingleChannel} is achieved
in a very straight-forward way by summing the correlation result over the channels.
